Master's thesis Computer Science\\ (Chair: Databases, Track: Information System Engineering)

### 2014-09-29 report/FrontBackmatter/Preface.tex
consistentie in Sander's titel
Dolf er ook in

Many thanks go to Dr. ir. Djoerd Hiemstra from the University of Twente and to Sander Bockting Msc. of Avanade Netherlands B.V. for their great supervision throughout the project. Even though we kept face-to-face meetings to a very minimum, you both provided me with very insightful and valuable feedback either in those meetings or per e-mail.\\

>>>>

Many thanks go to Dr. ir. Djoerd Hiemstra from the University of Twente and to Sander Bockting Msc of Avanade Netherlands B.V. for their great supervision throughout the project. Even though we kept face-to-face meetings to a very minimum, you both provided me with very insightful and valuable feedback either in those meetings or per e-mail. Also, I would like to thank Dr. ir. Dolf Trieschnigg, together with Djoerd and Sander a member of the assessment committee of this graduation project, for still being available for the role as second assessor of this work, while having joined the process rather late.\\
